---
title: "Stats_Week1_HW"
format: html
editor: visual
---

## Hello From Hong

I am a first-year PhD in the Joint Program of Public Policy and Sociology. My research interests are migration, higher education and social mobility. I have taken two quarters of social statistics at UCLA; however, it has been 2 years, and my memory has faded quickly. I have done some qualitative research but have not yet had the opportunity to apply my quantitative skill to real research projects. I hope to gain practical experience in quantitative research through this statistics series.

### Library Package

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(gapminder)
library(tinytable)
library(knitr)
library(kableExtra)

theme_set(theme_light())
```

### Data

```{r}
d <- gapminder
ds <- d |>
  filter(year == 1992) #keep 1992

```

### 

## Univariate plots

## 

```{r}
# density plot
ggplot(ds,
       aes(lifeExp))+
  geom_density()
```

## 

```{r}
# histogram
ggplot(ds,
       aes(lifeExp))+
  geom_histogram(binwidth = 5,
                 boundary = 0,
                 color = "blue")
```

## 

```{r}
#histogram
ggplot(ds,
       aes(pop))+
  geom_histogram(binwidth = 10000000,
                 boundary = 0,
                 color = "blue")
```

## 

```{r}
# bar graph
ggplot(ds,
       aes(x = continent))+
  geom_bar()
```

## Bivariate plots

## 

```{r}
# scatterplot
ggplot(ds,
       aes(x = gdpPercap,
           y = lifeExp))+
  geom_point()
```

## 

```{r}
# bar graph
ds |> 
  group_by(continent) |>
  summarize (Life = mean(lifeExp)) |>
ggplot(aes(x = continent,
           y = Life))+
  geom_bar(stat = "identity")
```

## 

```{r}
# strip plot
ggplot(ds,
       aes(x = pop,
       y = continent))+
  geom_point(alpha=0.8)
```

## 

```{r}
#strip plot
ggplot(ds,
       aes(x = pop,
           y = continent))+
  geom_jitter(height = 0.3,
              width = 0.3,
              alpha= 0.3)
```

## Time Plots (Bivariate)

I will go back to full data to see trends in Asia

```{r}
Asia_plot <- d |>
  filter (continent == "Asia") |>
  ggplot(aes(x = year,
             y = gdpPercap,
             group = country,
             color = country))+
  geom_line()
```

```{r}
Asia_plot
```

## 

::: r-fit-text
My work is done!
:::
